# knitr Reproducible Research: Peer Assessment 1 Document
Wayne S. Lewis

## Introduction
Peer Assessment 1 involves analysis and visualization of a personal movement activity monitoring data set.

---
output: 
  html_document:
    keep_md: true
---
## Loading and preprocessing the data

First we load the data and add a column named "day" for the date in POSIXct format. We note, for example, that some days, like October 8, 2012, no readings were recorded.

```{r load & process, echo=TRUE}

library(dplyr, histogram)
## library(xtable)
u <- read.csv("activity.csv")
v <- transform(u, date = as.POSIXct(date))
v[which(v$date=="2012-10-08"), 1]

```

## What is mean total number of steps taken per day?

We find the total number of steps taken per day and display the totals in a histogram..

```{r histogram, echo=TRUE}

days <- group_by(v, date)
w <- summarize(days, sum = sum(steps), mean = mean(steps,na.rm=T), median = median(steps,na.rm=T))
hist(w$sum, col='blue', main="Steps Per Day",xlab="Steps", ylab="Days")

```

We display in a table the mean and the median number of steps taken each day. The mean on October 8, 2012, for example, displays "NaN" for the mean - this occurs when the "na.rm=TRUE" option is used for the mean when all the values are "NA".

```{r setup, include=FALSE}

library(xtable)
source("styles.R")
options(rstudio.markdownToHTML = 
       function(inputFile, outputFile) {      
       require(markdown)
       markdownToHTML(inputFile, outputFile, stylesheet='custom.css')   
      }
)

xtable <- function(x, ...) {
   for (i in which(sapply(x, function(y) !all(is.na(match(c("POSIXct"),class(y))))))) x[[i]] <- as.character(x[[i]])
   xtable::xtable(x, ...)
                           }

```

```{r means & medians table, results="asis", echo=TRUE}

xt <- xtable(select(w, date, sum, mean, median))
print(xt, type = "html", include.rownames=FALSE)

```



## What is the average daily activity pattern?




## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?



hist(x$day, col='blue', breaks="days", main="Total Steps Per Day",xlab="", ylab="Steps")
t <- View(select(w, date, mean, median))
print(t, type="html")

xtable <- function(x, ...) {
   for (i in which(sapply(x, function(y) !all(is.na(match(c("POSIXt","POSIXct","Date"),class(y))))))) x[[i]] <- as.character(x[[i]])
   xtable::xtable(x, ...)
}



